Fractional Decomposition Tree Algorithm: A tool for studying the integrality gap of Integer Programs

### 2020-08-08 FDT2020/main-section.tex
Few small edits

Let $O_i$ be the set of odd-degree vertices of spanning tree $T_i$. Now consider the incidence vectors of feasible $O_i$-joins. Consider any subset of vertices $S$ with an even number of odd-degree vertices.  Then the $O_i$-join LP requires at least one edge joining $S$ to the rest of the vertices. The subtour-elimination LP requires every subset of vertices have two edges connecting it to the rest of the graph.  Therefore, since $x$ is a feasible solution to the subtour-elimination LP, then $x/2$ is feasible for the $O_i$-join associated with spanning tree $T_i$.
Thus we have $\frac{x}{2}$ is in the convex hull of incidence vectors of $O_i$-join of $G$, denoted $O_i\join(G)$.
%\cindy{There was another instance of ``It's easy to see that...'' Given that (quite reasonably) you do not expect the reader to know what an O-join is, you should probably just give the short justification for this statement and remove ``It's easy to see that.''}

@@

 We solve the following LP that allows us to find parity corrections that are good for the whole convex combination.
\begin{equation}\label{ojoinaverage}
\min \{ \alpha:\;\sum_{i=1}^{k} \lambda_i y^i = \alpha \cdot x,\;  y^i \in O_i\join(G) \; \mbox{for $i\in [k]$}\}.
\end{equation}
The variables in the above LP are $y^i\in \mathbb{R}^{E_x}_{
\geq 0}$ for $i\in [k]$. For each $i\in [k]$ we have $y^i\in O_i\join(G_x)$.
\cindy{You say the $y^i$ are LP variables, not integers. It even looks like they can even be more than $1$. What does it mean for a non-binary vector to be in a set of binary variables?  I would have expected the lambdas to be the variables, given their use as the convex combination multipliers in most of the paper.}
This formulation allows the instance-specific approximation ratio of Christofides' algorithm to be below $\frac{3}{2}$. Recall that a Carr-Vempala point consists of a single cycle of fractional edges.  Figure \ref{fdtvschris} shows FDT's solutions on all Carr-Vempala points that have 10 vertices on the cycle formed by fractional edges. We show for these points the apporoximation factor provided by FDT is always better than those from the polyhedral version of Christofides' algorithm. In Figure \ref{fdtvschris} the horizontal axis of the plot is indexed with the 60 Carr-Vempala points that we considered. For each Carr-Vempala point $x$, there are two data points. The value of the first data point depicted by a circle on the vertical axis is $\frac{|V|-1}{|V|}+\alpha$  and $\alpha$ is the optimal solution to (\ref{ojoinaverage}). \cindy{TODO: say when giving the LP~(\ref{ojoinaverage}) how that gives a solution to TAP with this value.}
The value of the second data point depicted by a cross on the vertical axis is $C$ where $C$ is obtained from applying Theorem \ref{FDT2EC} to $x$. In other words, Figure \ref{fdtvschris} is comparing the instance-specific upper bound on integrality gap certified by Christofides' algorithm to the approximation factor of the FDT algorithm for 2EC.

>>>>

Let $O_i$ be the set of odd-degree vertices of spanning tree $T_i$. Consider the incidence vectors of feasible $O_i$-joins. Let $S$ be any subset of vertices with an even number of odd-degree vertices.  The $O_i$-join LP requires at least one edge joining $S$ to the rest of the vertices. The subtour-elimination LP requires every subset of vertices have two edges connecting it to the rest of the vertices.  Therefore, since $x$ is a feasible solution to the subtour-elimination LP, $x/2$ is feasible for the $O_i$-join LP associated with spanning tree $T_i$.
That is, $\frac{x}{2}$ is in the convex hull of incidence vectors of $O_i$-join of $G$, denoted $O_i\join(G)$.
%\cindy{There was another instance of ``It's easy to see that...'' Given that (quite reasonably) you do not expect the reader to know what an O-join is, you should probably just give the short justification for this statement and remove ``It's easy to see that.''}

@@

 We solve the following LP that allows us to find parity corrections that are good for the whole convex combination.
\begin{equation}\label{ojoinaverage}
\min \{ \alpha:\;\sum_{i=1}^{k} \lambda_i y^i = \alpha \cdot x,\;  y^i \in O_i\join(G) \; \mbox{for $i\in [k]$}\}.
\end{equation}
The variables in the above LP are $y^i\in \mathbb{R}^{E_x}_{
\geq 0}$ for $i\in [k]$. For each $i\in [k]$ we have $y^i\in O_i\join(G_x)$.
\cindy{You say the $y^i$ are LP variables, not integers. It even looks like they can even be more than $1$. What does it mean for a non-binary vector to be in a set of binary variables?  I would have expected the lambdas to be the variables, given their use as the convex combination multipliers in most of the paper.}
This formulation allows the instance-specific approximation ratio of Christofides' algorithm to be below $\frac{3}{2}$.

%Recall that a Carr-Vempala point consists of a single cycle of fractional edges.
Figure \ref{fdtvschris} shows FDT's solutions on all Carr-Vempala points that have 10 vertices on the cycle formed by fractional edges. We show for these points the apporoximation factor provided by FDT is always better than those from the polyhedral version of Christofides' algorithm. In Figure \ref{fdtvschris} the horizontal axis of the plot is indexed with the 60 Carr-Vempala points that we considered. For each Carr-Vempala point $x$, there are two data points. The value of the first data point depicted by a circle on the vertical axis is $\frac{|V|-1}{|V|}+\alpha$  and $\alpha$ is the optimal solution to (\ref{ojoinaverage}). \cindy{TODO: say when giving the LP~(\ref{ojoinaverage}) how that gives a solution to TAP with this value.}
The value of the second data point depicted by a cross on the vertical axis is $C$ where $C$ is obtained from applying Theorem \ref{FDT2EC} to $x$. In other words, Figure \ref{fdtvschris} is comparing the instance-specific upper bound on integrality gap certified by Christofides' algorithm to the approximation factor of the FDT algorithm for 2EC.
